Prediction of PIK3CA mutation with gene expression

### 2020-04-08 plosOne/plosOne.Rmd
aupr figure

---
title: Prediction of PIK3CA mutation with gene expression
author:
  - name: Jun Kang
    email: jkang.alien@gmail.com
    affiliation: Department of Hospital Pathology, Seoul St. Mary’s Hospital, College of Medicine, The Catholic University of Korea, Seoul, South Korea
    corresponding: jkang.alien@gmail.com

abstract: |

bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

>>>>

---
title: Prediction of PIK3CA mutation with gene expression
author:
  - name: Jun Kang
    email: jkang.alien@gmail.com
    affiliation: Department of Hospital Pathology, Seoul St. Mary’s Hospital, College of Medicine, The Catholic University of Korea, Seoul, South Korea
    corresponding: jkang.alien@gmail.com
abstract: |
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

@@

PIK3CA prediction model performed better than RAS activation prediction model in terms of AUROC. The overall AUPR was

### 2020-04-08 plosOne/plosOne.tex
aupr figure

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Prediction of PIK3CA mutation with gene expression} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jun Kang\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital, College of
Medicine, The Catholic University of Korea, Seoul, South Korea}}\textsuperscript{*}\\
\bigskip
\bigskip
* Corresponding author: jkang.alien@gmail.com\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget
porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut
dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id
velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus
finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium
diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut
ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit
pulvinar, volutpat risus.

@@

@@

@@

\hypertarget{figure-legends}{%
\section*{Figure legends}\label{figure-legends}}
\addcontentsline{toc}{section}{Figure legends}

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Prediction of PIK3CA mutation with gene expression} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jun Kang\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital, College of
Medicine, The Catholic University of Korea, Seoul, South Korea}}\textsuperscript{*}\\
\bigskip
\bigskip
* Corresponding author: jkang.alien@gmail.com\\
\end{flushleft}
% Please keep the abstract below 300 words

@@

The trainset AUROC was 0.93 and the testset AUROC was 0.84. The AUPR of
trainset was 0.74 and the testset AUPR was 0.771.

@@

\hypertarget{figure-legends}{%
\section{Figure legends}\label{figure-legends}}

Figure 1. Summary of modeling results

\begin{enumerate}
\def\labelenumi{(\Alph{enumi})}
\tightlist
\item
  Left: receiver operating characteristic (ROC) curve right: precision
  recall (PR) curve of trainset and testset. The horizontal green line
  is the PIK3CA mutation rate (0.11) (B) Correlation between trainset
  and testset of area under receiver operating characteristic curve
  (AUROC) and area under precision recall curve (AUPR) among cancer
  type. The abbreviations are explained in S1 appendix. (C) Correlation
  between the PIK3CA mutation rate of area under receiver operating
  characteristic curve (AUROC) and area under precision recall curve
  (AUPR).
\end{enumerate}

Figure 2. Coefficients of model

\begin{enumerate}
\def\labelenumi{(\Alph{enumi})}
\tightlist
\item
  Top 30 high coefficients of mRNA. (B) Coefficients of cancer types.
  The abbreviations are explained in S1 appendix.
\end{enumerate}

\hypertarget{supporting-information}{%
\section{Supporting information}\label{supporting-information}}

S1 Appendix. S2 Figure. S1 Table.\\
S2 Table.\\
S3 Table.

@@
